IMPC Mouse data - Variance in sex differences

### 2019-11-06 Prep & old/prep and old- scripts/IMPC variance and sex difference May15_2019_FZ3-6-19.Rmd
Update Nov

---
title: "IMPC Mouse data - Variance in sex differences"
author: "Susanne & Felix Zajitschek"
date: "2nd April 2019"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
    toc_depth: 3
runtime: shiny
---

@@

# Loading functions that are necessary
### Preparation of raw data
1) Data loading and cleaning of the csv file
This step we have already done and provide a cleaned up file which is less computing intensive. However, cvs
```{r}

@@

Calc.var.lnCVR <- function(CMean, CSD, CN, EMean, ESD, EN, Equal.E.C.Corr=T) {
  if(Equal.E.C.Corr==T){
    mvcorr <- 0 #cor.test(log(c(CMean, EMean)), log(c(CSD, ESD)))$estimate   old, slightly incorrect
    S2 <- CSD^2 / (CN * (CMean^2)) + 1 / (2 * (CN - 1)) - 2 * mvcorr * sqrt((CSD^2 / (CN * (CMean^2))) * (1 / (2 * (CN - 1)))) + ESD^2 / (EN * (EMean^2)) + 1 / (2 * (EN - 1)) - 2 * mvcorr * sqrt((ESD^2 / (EN * (EMean^2))) * (1 / (2 * (EN - 1))))
  }
  else{
    Cmvcorr <- cor.test(log(CMean), log(CSD))$estimate
    Emvcorr <- cor.test(log(EMean), (ESD))$estimate
    S2 <- CSD^2 / (CN * (CMean^2)) + 1 / (2 * (CN - 1)) - 2 * Cmvcorr * sqrt((CSD^2 / (CN * (CMean^2))) * (1 / (2 * (CN - 1)))) + ESD^2 / (EN * (EMean^2)) + 1 / (2 * (EN - 1)) - 2 * Emvcorr * sqrt((ESD^2 / (EN * (EMean^2))) * (1 / (2 * (EN - 1))))		
  }
  S2
}

@@

We here provide the cleaned dataset, which we have saved in a folder called "export", as easy starting point. However, the full dataset can be loaded and cleaned using the data cleaning function (Function 1 above), if "#" signs in the code below are removed  (created as that is much smaller than the .csv - which we can still provide for those who absolutely want to start from scratch?)
```{r}
## Load raw data - save cleaned dataset as RDS for reuse
#data_raw <- load_raw("data/dr7.0_all_control_data.csv") %>%
#    clean_raw_data()
#dir.create("export", F, F)
#saveRDS(data_raw, "export/data_clean.rds")

@@

### Clean data
This requires the selection of traits that have been measured in at least 2 centers. Consequently, rare or unusual methods and procedures are being filtered out in this step.
```{r }
dat1 <-
  data1 %>%
  group_by(parameter_name) %>%
  summarize(center_per_trait = length(unique(production_center, na.rm = TRUE)))

@@

### Create a matrix to store results for all traits
As the current version of this script utilizes a loop instead of tidyR code, it is here necessary to create an empty matrix, in which the returning values will be stored.

```{r}
results.alltraits.grouping <- as.data.frame(cbind(c(1:n), matrix(rep(0, n*14), ncol = 14))) #number of individual results per trait = 10
names(results.alltraits.grouping) <- c("id", "lnCVR", "lnCVR_lower", "lnCVR_upper", "lnCVR_se", "lnVR", "lnVR_lower", "lnVR_upper", "lnVR_se", "lnRR", "lnRR_lower", "lnRR_upper" ,"lnRR_se" , "sampleSize", "trait")
```

## LOOP, to run meta-analysis on all traits
The loop combines the functions mentioned above and fills the data matrix with results from our meta analysis. 
Error messages indicate traits that either did not reach convergence, or that did not return meaningful results in the meta-analysis, due to absence of variance. Those traits will be removed in later steps, outlined below.

@@

#lnCVR,  log repsonse-ratio of the coefficient of variance    
    cvr <- metafor::rma.mv(yi = effect_size_CVR, V = sample_variance_CVR, random = list(~1| strain_name, ~1|production_center, ~1|err), control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000),  verbose=F, data = results)

    results.alltraits.grouping[t, 2] <- cvr$b
    results.alltraits.grouping[t, 3] <- cvr$ci.lb
    results.alltraits.grouping[t, 4] <- cvr$ci.ub
    results.alltraits.grouping[t, 5] <- cvr$se

@@

cv <- metafor::rma.mv(yi = effect_size_VR, V = sample_variance_VR, random = list(~1| strain_name, ~1|production_center,~1|err), control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000),  verbose=F, data = results)

    results.alltraits.grouping[t, 6] <- cv$b
    results.alltraits.grouping[t, 7] <- cv$ci.lb
    results.alltraits.grouping[t, 8] <- cv$ci.ub
    results.alltraits.grouping[t, 9] <- cv$se

@@

        results.alltraits.grouping[t, 14] <- means$k
        results.alltraits.grouping[t, 15] <- unique(results$trait)

@@

# Now that we have a "results" table with each of the meta-analytic means for all effect sizes of interest, we can use this table as part of the Shint App, which will then be able to back calculate the percentage differences between males and females for mean, variance and coefficient of variance. We'll export and use this in the Shiny App. **Note that I have not dealt with convergence issues in some of these models, and so, this will need to be done down the road**

trait_meta_results <- write.csv(results.alltraits.grouping, file = "export/trait_meta_results.csv")

@@

### Merging datasets

Procedure names, grouping variables etc. are merged back together with the results from the metafor analysis above.
This requires loading of another excel sheet, "procedures.csv"

```{r}
procedures <- read.csv("export/procedures.csv")

@@

Removal of traits that did not achieve convergence, are nonsensical for analysis of variance (such as traits that show variation, such as number of ribs, digits, etc). 14 traits from the originally 232 that had been included are removed.

@@

## Dealing with Correlated Parameters

This dataset contained a number of highly correlated traits, such as different kinds of cell counts (for example, hierarchical parametrization within immunological assays). As those data-points are not independent of each other,  we conducted a meta analyses on these correlated parameters to collapse the number of levels.

### Collapsing correlated parameters

@@

### Count of number of parameter names (correlated sub-traits) in each parameter group (par_group_size) 
This serves to identify and separate the traits that are correlated from the full dataset that can be processed as is. If the sample size (n) for a given "parameter group" equals 1, the trait is unique and uncorrelated. All instances, where there are 2 or more traits associated with the same  parameter group (90 cases), are selected for a "mini-meta analysis", which removes the issue of correlation.

@@

### Perform meta-analyses on correlated sub-traits, using `robumeta` 
The subset of the data is prepared (nested), and in this first step the model of the meta analysis effect sizes are calculated

@@

### Extract and save parameter estimates 
Function to collect the outcomes of the "mini" meta analysis
```{r}
count_fun <- function(mod_sub)
  return(c(mod_sub$reg_table$b.r, mod_sub$reg_table$CI.L, mod_sub$reg_table$CI.U, mod_sub$reg_table$SE))   #estimate, lower ci, upper ci, SE
```

Extraction of values created during Meta analysis using robu meta
```{r}
robusub_RR <- model_count %>% 
  transmute(parameter_group, estimatelnRR = map(model_lnRR, count_fun)) %>% 
  mutate(r = map(estimatelnRR, ~ data.frame(t(.)))) %>%
  unnest(r) %>%
  select(-estimatelnRR) %>%
  purrr::set_names(c("parameter_group","lnRR","lnRR_lower","lnRR_upper","lnRR_se"))

@@

 Merge the two data sets (the new [robu_all] and the initial [uncorrelated sub-traits with count = 1]) 
```{r}
meta_all <- meta1 %>% filter(par_group_size == 1) %>% as_tibble
#str(meta_all)
#str(robu_all)
#which(is.na(match(names(meta_all),names(robu_all))))  # check
```

Combine data 
```{r}
# Step1 
combinedmeta <- bind_rows(robu_all, meta_all)
#glimpse(combinedmeta)

@@

```
### Clean-up and rename 
```{r}
metacombo <-metacombo[, c(1, 20:22, 2:13)] 
names(metacombo)[3] <- "procedure" 
names(metacombo)[4] <- "GroupingTerm"

@@

## Last step: meta-meta-analysis 
### Perform meta-analyses (3 for each of the 9 grouping terms: lnCVR, lnVR, lnRR) 
This is the full result dataset
```{r}

@@

### Prepare data
Nesting, calculating the number of parameters within each grouping term, and running the meta-analysis
```{r}
metacombo_final <- metacombo %>%
 group_by(GroupingTerm) %>%
 nest()

@@

Re-structure data for each grouping term; delete unused variables

@@

## Plot FIGURE 2 (First-order meta analysis results)

Re-order grouping terms

@@

### Prepare data for traits with CI not overlapping 0
create column with 1= different from zero, 0= zero included in CI
```{r}

@@

Prepare data for traits with effect size ratios > 10% larger in males
```{r}
meta.plot2.over10 <- meta_clean %>% select(lnCVR, lnVR, lnRR, GroupingTerm) %>% arrange(GroupingTerm)

@@

```
### Create final combined Figure (Figure 2)
```{r}

@@

## Preparation, for Figure 3: Overall results of second order meta anlaysis
### Restructure data for plotting 
Data are restructured, and grouping terms are being re-ordered
```{r}
overall3 <- gather(overall2, parameter, value, c(lnCVR, lnVR, lnRR), factor_key= TRUE)

@@

### Plot FIGURE 3 (Second-order meta analysis results)

Preparation: Sub-Plot  for Figure 3: all traits
```{r}

@@

### Prepare data for traits with CI not overlapping 0

create column with 1= different from zero, 0= zero included in CI
Male-biased (significant) traits
```{r}
meta.male.plot3.sig <- metacombo %>% 
    	mutate(sigCVR = ifelse(lnCVR_lower > 0, 1, 0),
	sigVR = ifelse(lnVR_lower > 0, 1, 0),
	sigRR = ifelse(lnRR_lower > 0, 1, 0))

@@

plot3.male.meta.CVR.b <- as.data.frame(plot3.male.meta.CVR %>% group_by(GroupingTerm) %>%  
		mutate(lnCVR = map_dbl(model_lnCVR, pluck(2)), lnCVR_lower = map_dbl(model_lnCVR, pluck(6)), 
		lnCVR_upper =map_dbl(model_lnCVR, pluck(7)), lnCVR_se =map_dbl(model_lnCVR, pluck(3))) )[, c(1,4:7)] 
add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.male.meta.CVR.b))

plot3.male.meta.CVR.b <- bind_rows(plot3.male.meta.CVR.b, add.row.hearing) 
plot3.male.meta.CVR.b <- plot3.male.meta.CVR.b[order(plot3.male.meta.CVR.b$GroupingTerm),]

@@

Restructure MALE data for plotting 
```{r}
overall3.male.sig <- gather(overall.male.plot3, parameter, value, c(lnCVR, lnVR, lnRR), factor_key= TRUE)

@@

Plot Fig3 all significant results (CI not overlapping zero) for males
```{r}
######

Metameta_Fig3_male.sig <- overall4.male.sig %>%
  ggplot(aes(y= GroupingTerm, x= value)) +
  geom_errorbarh(aes(xmin = ci.low, 
                     xmax = ci.high), 
			   height = 0.1, show.legend = FALSE) +
  geom_point(aes(shape = parameter),
             fill = 'mediumaquamarine', color = 'mediumaquamarine', size = 2.2, 
               show.legend = FALSE) +
  scale_x_continuous(limits=c(0, 0.4), 
                     breaks = c(0, 0.3), 
                     name='Effect size') +
  geom_vline(xintercept=0, 
             color='black', 
             linetype='dashed')+
  facet_grid(cols = vars(parameter), rows = vars(label),
             labeller = label_wrap_gen(width = 23),
             scales= 'free', 
             space='free')+
  theme_bw()+
  theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
	  strip.text.x = element_text(size = 12),
        strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
        text = element_text(size = 14),
        panel.spacing = unit(0.5, "lines"),
        panel.border= element_blank(),
        axis.line=element_line(), 
        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(), 
        legend.title = element_blank(),
        axis.title.x = element_blank(),
	  axis.title.y = element_blank())

@@

#######################
### Female Figure
Female Fig3 sig

Prepare data for traits with CI not overlapping 0
create column with 1= different from zero, 0= zero included in CI
```{r}

@@

add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.female.meta.CVR.b))

plot3.female.meta.CVR.b <- bind_rows(plot3.female.meta.CVR.b, add.row.hearing)
plot3.female.meta.CVR.b <- plot3.female.meta.CVR.b[order(plot3.female.meta.CVR.b$GroupingTerm),]

@@

overall.female.plot3 <- full_join(plot3.female.meta.CVR.b, plot3.female.meta.VR.b)
overall.female.plot3 <- full_join(overall.female.plot3, plot3.female.meta.RR.b)

@@

#add missing GroupingTerms for plot POYTENTIALLY DELETE
#overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Morphology")
#overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Metabolism")
#overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Hematology")
#overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Hearing")
#overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Eye")

#overall.female.plot3$GroupingTerm <- factor(overall.female.plot3$GroupingTerm, levels =c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All") )
#overall.female.plot3$GroupingTerm <- factor(overall.female.plot3$GroupingTerm, rev(levels(overall.female.plot3$GroupingTerm)))

@@

Restructure data for plotting

@@

### Plot Fig3 all significant results (CI not overlapping zero, female )
```{r}

Metameta_Fig3_female.sig <- overall4.female.sig %>%
  ggplot(aes(y= GroupingTerm, x= value)) +
  geom_errorbarh(aes(xmin = ci.low,
                     xmax = ci.high),
                     height = 0.1, show.legend = FALSE) +
  geom_point(aes(shape = parameter),
             fill = 'salmon1', color = 'salmon1', size = 2.2,
             show.legend = FALSE) +
  scale_x_continuous(limits=c(-0.4, 0),
                     breaks = c(-0.3 ,0),
                     name='Effect size') +
  geom_vline(xintercept=0,
             color='black',
             linetype='dashed')+
  facet_grid(cols = vars(parameter), #rows = vars(label),
             #labeller = label_wrap_gen(width = 23),
             scales= 'free',
             space='free')+
  theme_bw()+
  theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)),
                strip.text.x = element_text(size = 12),
        strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
        text = element_text(size = 14),
        panel.spacing = unit(0.5, "lines"),
        panel.border= element_blank(),
        axis.line=element_line(),
        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        legend.title = element_blank(),
        axis.title.x = element_blank(),
                axis.title.y = element_blank())

@@

### Fig3 >10%

Prepare data for traits with m/f difference > 10%

create column with 1= larger, 0= diff not larger than 10%

### Male Fig 3 > 10% (male biased traits)
```{r}
meta.male.plot3.perc <- metacombo %>% 
    	mutate(percCVR = ifelse(lnCVR > log (11/10), 1, 0),			
	percVR = ifelse(lnVR > log (11/10), 1, 0),
	percRR = ifelse(lnRR > log (11/10), 1, 0))

@@

overall.male.plot3.perc <- full_join(plot3.male.meta.CVR.perc.b, plot3.male.meta.VR.perc.b) 
overall.male.plot3.perc <- full_join(overall.male.plot3.perc, plot3.male.meta.RR.perc.b)

@@

Restructure data for plotting : Male biased, 10% difference
```{r}
overall3.perc <- gather(overall.male.plot3.perc, parameter, value, c(lnCVR, lnVR, lnRR), factor_key= TRUE)

@@

Plot Fig3 all >10% difference (male bias)
```{r}

>>>>

---
title: "IMPC Mouse data - Variance in sex differences"
author: "Susanne & Felix Zajitschek"
date: "2nd April 2019"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
    toc_depth: 3
---

@@

# Loading functions that are necessary
##Preparation of raw data
1) Data loading and cleaning of the csv file
This step we have already done and provide a the cleaned up file which is less computing intensive. However, cvs
```{r}

@@

Calc.var.lnCVR <- function(CMean, CSD, CN, EMean, ESD, EN, Equal.E.C.Corr=T) {
  if(Equal.E.C.Corr==T){
    mvcorr <- <-0 #cor.test(log(c(CMean, EMean)), log(c(CSD, ESD)))$estimate   old, slightly incorrect
    S2 <- CSD^2 / (CN * (CMean^2)) + 1 / (2 * (CN - 1)) - 2 * mvcorr * sqrt((CSD^2 / (CN * (CMean^2))) * (1 / (2 * (CN - 1)))) + ESD^2 / (EN * (EMean^2)) + 1 / (2 * (EN - 1)) - 2 * mvcorr * sqrt((ESD^2 / (EN * (EMean^2))) * (1 / (2 * (EN - 1))))
  }
  else{
    Cmvcorr <- cor.test(log(CMean), log(CSD))$estimate
    Emvcorr <- cor.test(log(EMean), (ESD))$estimate
    S2 <- CSD^2 / (CN * (CMean^2)) + 1 / (2 * (CN - 1)) - 2 * Cmvcorr * sqrt((CSD^2 / (CN * (CMean^2))) * (1 / (2 * (CN - 1)))) + ESD^2 / (EN * (EMean^2)) + 1 / (2 * (EN - 1)) - 2 * Emvcorr * sqrt((ESD^2 / (EN * (EMean^2))) * (1 / (2 * (EN - 1))))		
  }
  S2
}

@@

We here provide the cleaned dataset, which we have saved in a folder called "export", as easy starting point. However, the full dataset can ve loaded and cleaned using the da cleaning function (Function 1 above), if "#" signs in the code below are removed  (created as that is much smaller than th e .csv - which we can still provide for those who absoliutely want to start from scratch?)
```{r}
## Load raw data - save cleaned dataset as RDS for reuse
#data_raw <- load_raw("data/dr7.0_all_control_data.csv") %>%
#    clean_raw_data()
#dir.create("export", F, F)
#saveRDS(data_raw, "export/data_clean.rds")

@@

## Clean data
This requires the selection of traits that have been measured in at least 2 centers. Consequently, rare or unusual methods and procedures are being filtered out in this step.
```{r }
dat1 <-
  data1 %>%
  group_by(parameter_name) %>%
  summarize(center_per_trait = length(unique(production_center, na.rm = TRUE)))

@@

## Create a matrix to store results for all traits
As the current version of this script utilizes a loop instead of tidyR code, it is here necessary to create an empty matrix, in which the returning values will be stored.

```{r}
results.alltraits.grouping <- as.data.frame(cbind(c(1:n), matrix(rep(0, n*13), ncol = 13))) #number of individual results per trait = 10
names(results.alltraits.grouping) <- c("id", "lnCVR", "lnCVR_lower", "lnCVR_upper", "lnCVR_se", "lnVR", "lnVR_lower", "lnVR_upper", "lnVR_se", "lnRR", "lnRR_lower", "lnRR_upper" ,"lnRR_se" , "sampleSize")

# LOOP, to run meta-analysis on all traits
The loop combines the functions menationed above and fills the data matrix with results from our meta analysis. 
Error messages indicate traits that either did not reach convergence, or that did not return meaningful results in the metaanalysis, due to absence of variance. Those traits will be removed ion later steps, outlined below.

@@

#lnCVR,  log repsonse-ratio of the coefficient of variance    
    cvr <- metafor::rma.mv(yi = effect_size_CVR, V = sample_variance_CVR, random = list(~1| strain_name, ~1|production_center,    
                                                                                        ~1|err), control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000), data = results)
    results.alltraits.grouping[t, 2] <- cvr$b
    results.alltraits.grouping[t, 3] <- cvr$ci.lb
    results.alltraits.grouping[t, 4] <- cvr$ci.ub
    results.alltraits.grouping[t, 5] <- cvr$se

@@

cv <- metafor::rma.mv(yi = effect_size_VR, V = sample_variance_VR, random = list(~1| strain_name, ~1|production_center,                                                             ~1|err), control=list(optimizer="optim", optmethod="Nelder-Mead", maxit= 1000),  verbose=F, data = results)
    results.alltraits.grouping[t, 6] <- cv$b
    results.alltraits.grouping[t, 7] <- cv$ci.lb
    results.alltraits.grouping[t, 8] <- cv$ci.ub
    results.alltraits.grouping[t, 9] <- cv$se

@@

        results.alltraits.grouping[t, 14] <- means$k

@@

@@

# Merging datasets

Procedure names, groupiung variables etc are merged back together with the results from the metafor analysis above.
This requires loading of another excel sheet, "procedures.csv"

@@

Removal of traits that did not achieve convergence, are non-sensical for analysis of variance (such as traits that show variaton, such as number of ribs, digits, etc). 14 traits from the originally 232 that had been included are removed.

@@

#Dealing with Correlated Paramters

This dataset contained a number of highly correlated taits, such as different kinds of cell counts (for example, hierarchichal parametrization within immunologocal assays). As those datapoints are not independent of each other,  we conducted a meta analyses on these correlated parameters to collapse the number of levels.

## Collapsing correlated parameters

@@

## Count of number of parameter names (correlated sub-traits) in each parameter group (par_group_size) 
This serves to idenfify and separate the traits that are correlated from the full dataset that can be preocessed as is. If the sample size (n) for a given "parameter group" equals 1, the trait is unique and uncorrelated. All instances, where there are 2 or more traits accociated with the same  parameter group (90 cases), are selected for a "mini-meta analysis", which removes the issue of correlation.

@@

## Perform meta-analyses on correlated sub-traits, using robumeta 
The subset of the data is prepared (nested), and in this first step the model of the meta analysis effect sizes are calculated

@@

## Extract and save parameter estimates 
Function to collect the outcomes of the "mini" meta analysis
```{r}
count_fun <- function(mod_sub)
  return(c(mod_sub$reg_table$b.r, mod_sub$reg_table$CI.L, mod_sub$reg_table$CI.U, mod_sub$reg_table$SE))   #estimate, lower ci, upper ci, SE
```

Meta analysis using robu meta
```{r}
robusub_RR <- model_count %>% 
  transmute(parameter_group, estimatelnRR = map(model_lnRR, count_fun)) %>% 
  mutate(r = map(estimatelnRR, ~ data.frame(t(.)))) %>%
  unnest(r) %>%
  select(-estimatelnRR) %>%
  purrr::set_names(c("parameter_group","lnRR","lnRR_lower","lnRR_upper","lnRR_se"))

@@

## Merge the two data sets (the new [robu_all] and the initial [uncorrelated sub-traits with count = 1]) 
```{r}
meta_all <- meta1 %>% filter(par_group_size == 1) %>% as_tibble
#str(meta_all)
#str(robu_all)
#which(is.na(match(names(meta_all),names(robu_all))))  # check
```

# Combine data

```{r}
# Step1 
combinedmeta <- bind_rows(robu_all, meta_all)
#glimpse(combinedmeta)

@@

# Clean-up and rename 
```{r}
metacombo <-metacombo[, c(1, 20:22, 2:13)] 
names(metacombo)[3] <- "procedure" 
names(metacombo)[4] <- "GroupingTerm"

@@

# Last step: meta-meta-analysis 
## *Perform meta-analyses (3 for each of the 9 grouping terms: lnCVR, lnVR, lnRR) 
This is the full result dataset
```{r}

@@

# Prepare data
Nesting, calculating the number of parameters within each grouping term, and running the metaanalysis
```{r}
metacombo_final <- metacombo %>%
 group_by(GroupingTerm) %>%
 nest()

@@

# Re-structure data for each grouping term; delete un-used variables

@@

# **Plot FIGURE 2 (First-order meta analysis results)

@@

# *Prepare data for traits with CI not overlapping 0
##create column with 1= different from zero, 0= zero included in CI
```{r}

@@

# *Prepare data for traits with effect size ratios > 10% larger in males
```{r}
meta.plot2.over10 <- meta_clean %>% select(lnCVR, lnVR, lnRR, GroupingTerm) %>% arrange(GroupingTerm)

@@

```
Create final combined Figure
```{r}

@@

## Preparation, for Figure 3: Overall results of second order meta anlaysis
## Restructure data for plotting 
Data are restructred, and grouping terms are being re-ordered
```{r}
overall3 <- gather(overall2, parameter, value, c(lnCVR, lnVR, lnRR), factor_key= TRUE)

@@

# Plot FIGURE 3 (Second-order meta analysis results)

# Preparation: Sub-Plot  for Figure 3: all traits
```{r}

@@

# *Prepare data for traits with CI not overlapping 0

#create column with 1= different from zero, 0= zero included in CI
# ** Male-biased traits
```{r}
meta.male.plot3.sig <- metacombo %>% 
    	mutate(sigCVR = ifelse(lnCVR_lower > 0, 1, 0),
	sigVR = ifelse(lnVR_lower > 0, 1, 0),
	sigRR = ifelse(lnRR_lower > 0, 1, 0))

@@

plot3.male.meta.CVR.b <- as.data.frame(plot3.male.meta.CVR %>% group_by(GroupingTerm) %>%  
		mutate(lnCVR = map_dbl(model_lnCVR, pluck(2)), lnCVR_lower = map_dbl(model_lnCVR, pluck(6)), 
		lnCVR_upper =map_dbl(model_lnCVR, pluck(7)), lnCVR_se =map_dbl(model_lnCVR, pluck(3))) )[, c(1,4:7)] 
add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.male.meta.CVR.b))    
plot3.male.meta.CVR.b <- bind_rows(plot3.male.meta.CVR.b, add.row.hearing) 
plot3.male.meta.CVR.b <- plot3.male.meta.CVR.b[order(plot3.male.meta.CVR.b$GroupingTerm),]

@@

# **Restructure MALE data for plotting 
```{r}
overall3.male.sig <- gather(overall.male.plot3, parameter, value, c(lnCVR, lnVR, lnRR), factor_key= TRUE)

@@

# **Plot Fig3 all significant results (CI not overlapping zero) for males
```{r}
######

Metameta_Fig3_male.sig <- overall4.male.sig %>%
  ggplot(aes(y= GroupingTerm, x= value)) +
  geom_errorbarh(aes(xmin = ci.low, 
                     xmax = ci.high), 
			   height = 0.1, show.legend = FALSE) +
  geom_point(aes(shape = parameter),
             fill = 'blue', color = 'blue', size = 2.2,  #needs adjustment to nicer blue, 20-5-19
               show.legend = FALSE) +
  scale_x_continuous(limits=c(0, 0.4), 
                     breaks = c(0, 0.3), 
                     name='Effect size') +
  geom_vline(xintercept=0, 
             color='black', 
             linetype='dashed')+
  facet_grid(cols = vars(parameter), rows = vars(label),
             labeller = label_wrap_gen(width = 23),
             scales= 'free', 
             space='free')+
  theme_bw()+
  theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
	  strip.text.x = element_text(size = 12),
        strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
        text = element_text(size = 14),
        panel.spacing = unit(0.5, "lines"),
        panel.border= element_blank(),
        axis.line=element_line(), 
        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(), 
        legend.title = element_blank(),
        axis.title.x = element_blank(),
	  axis.title.y = element_blank())

@@

#######################
# **Female Fig3 sig

#*Prepare data for traits with CI not overlapping 0
create column with 1= different from zero, 0= zero included in CI
```{r}

@@

add.row.hearing <- as.data.frame(t(c("Hearing", NA, NA, NA, NA))) %>% setNames(names(plot3.female.meta.CVR.b))    
plot3.female.meta.CVR.b <- bind_rows(plot3.female.meta.CVR.b, add.row.hearing)
plot3.female.meta.CVR.b <- plot3.female.meta.CVR.b[order(plot3.female.meta.CVR.b$GroupingTerm),]

@@

overall.female.plot3 <- full_join(plot3.female.meta.CVR.b, plot3.female.meta.VR.b)  #FELIX: changed from inner to full
overall.female.plot3 <- full_join(overall.female.plot3, plot3.female.meta.RR.b)   #FELIX: changed from inner to full

@@

#add missing GroupingTerms for plot: NOT NEEDED (next 5 lines)FELIX
overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Morphology")
overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Metabolism")
overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Hematology")
overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Hearing")
overall.female.plot3 <- add_row(overall.female.plot3, GroupingTerm = "Eye")

NOT NEEDED (next 2 lines)FELIX
overall.female.plot3$GroupingTerm <- factor(overall.female.plot3$GroupingTerm, levels =c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All") )
overall.female.plot3$GroupingTerm <- factor(overall.female.plot3$GroupingTerm, rev(levels(overall.female.plot3$GroupingTerm)))

@@

# **Restructure data for plotting

@@

# **Plot Fig3 all significant results (CI not overlapping zero)
```{r}

Metameta_Fig3_female.sig <- overall4.female.sig %>%
  ggplot(aes(y= GroupingTerm, x= value)) +
  geom_errorbarh(aes(xmin = ci.low,
                     xmax = ci.high),
                     height = 0.1, show.legend = FALSE) +
  geom_point(aes(shape = parameter),
             fill = 'red', color = 'red', size = 2.2,
             show.legend = FALSE) +
  scale_x_continuous(limits=c(-0.4, 0),
                     breaks = c(-0.3 ,0),
                     name='Effect size') +
  geom_vline(xintercept=0,
             color='black',
             linetype='dashed')+
  facet_grid(cols = vars(parameter), #rows = vars(label),
             #labeller = label_wrap_gen(width = 23),
             scales= 'free',
             space='free')+
  theme_bw()+
  theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)),
                strip.text.x = element_text(size = 12),
        strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
        text = element_text(size = 14),
        panel.spacing = unit(0.5, "lines"),
        panel.border= element_blank(),
        axis.line=element_line(),
        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        legend.title = element_blank(),
        axis.title.x = element_blank(),
                axis.title.y = element_blank())

@@

# *Fig3 >10%

# *Prepare data for traits with m/f difference > 10%

#create column with 1= larger, 0= diff not larger than 10%

# Male Fig 3 > 10% (male biased traits)
```{r}
meta.male.plot3.perc <- metacombo %>% 
    	mutate(percCVR = ifelse(lnCVR > log (11/10), 1, 0),			
	percVR = ifelse(lnVR > log (11/10), 1, 0),
	percRR = ifelse(lnRR > log (11/10), 1, 0))

@@

overall.male.plot3.perc <- full_join(plot3.male.meta.CVR.perc.b, plot3.male.meta.VR.perc.b) #FELIX: changed inner to full
overall.male.plot3.perc <- full_join(overall.male.plot3.perc, plot3.male.meta.RR.perc.b)  #FELIX: changed inner to full

#FELIX: remove next 2 lines!
overall.male.plot3.perc$GroupingTerm <- factor(overall.male.plot3.perc$GroupingTerm, levels =c("Behaviour","Morphology","Metabolism","Physiology","Immunology","Hematology","Heart","Hearing","Eye", "All") )
overall.male.plot3.perc$GroupingTerm <- factor(overall.male.plot3.perc$GroupingTerm, rev(levels(overall.male.plot3.perc$GroupingTerm)))

#add missing GroupingTerms for plot
overall.male.plot3.perc <- add_row(overall.male.plot3.perc, GroupingTerm = "Heart")  #FELIX: delete this line
overall.male.plot3.perc <- add_row(overall.male.plot3.perc, GroupingTerm = "Eye")

@@

# **Restructure data for plotting : Male biased, 10% difference
```{r}
overall3.perc <- gather(overall.male.plot3.perc, parameter, value, c(lnCVR, lnVR, lnRR), factor_key= TRUE)

@@

# **Plot Fig3 all >10% difference (male bias)
```{r}

Metameta_Fig3_male.perc <- overall4.male.perc %>% filter(., GroupingTerm != "Hearing") %>%
  ggplot(aes(y= GroupingTerm, x= value)) +
  geom_errorbarh(aes(xmin = ci.low, 
                     xmax = ci.high), 
			   height = 0.1, show.legend = FALSE) +
  geom_point(aes(shape = parameter,
             fill = parameter), color = 'blue', size = 2.2, 
             show.legend = FALSE) +
  scale_x_continuous(limits=c(-0.2, 0.62), 
                     breaks = c(0, 0.3), 
                     name='Effect size') +
  geom_vline(xintercept=0, 
             color='black', 
             linetype='dashed')+
  facet_grid(cols = vars(parameter), rows = vars(label),
             labeller = label_wrap_gen(width = 23),
             scales= 'free', 
             space='free')+
  theme_bw()+
  theme(strip.text.y = element_text(angle = 270, size = 10, margin = margin(t=15, r=15, b=15, l=15)), 
	  strip.text.x = element_blank(),
        strip.background = element_rect(colour = NULL, linetype = "blank", fill = "gray90"),
        text = element_text(size = 14),
        panel.spacing = unit(0.5, "lines"),
        panel.border= element_blank(),
        axis.line=element_line(), 
        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(), 
        legend.title = element_blank(),
        axis.title.x = element_text(hjust = 0.5, size = 14),
	  axis.title.y = element_blank())
